Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-07-28 ms.tex
plots for many apertures

>>>>

\begin{figure*}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn487Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{}}}
{\gridline{\fig{ap_labels_azlab04LED1p5mAStripe64ManyApn489Rpt2_NRC64STRIPE1P5MA.pdf}{0.7\textwidth}{Apertures}}}
{\gridline{\fig{phot_azlab04LED1p5mAStripe64ManyApn_bothDetectors_Rpt2_NRC64STRIPE1P5MA_bin.pdf}{0.7\textwidth}{Time Series of Apertures}}}
\caption{Time series for many apertures on each detector, binned into 70 equal bins.}\label{fig:manyApPerDetector}
\end{figure*}
